---
title: Scraping stock prices
author: Christopher Furu
date: '2018-09-04'
slug: scraping-stock-prices
categories: []
tags:
  - Investment portfolio
  - Python
  - R
output:
  blogdown::html_page:
    toc: true
---

```{r setup, include=FALSE}
library(reticulate)
library(knitr)
library(kableExtra)
```
# Introduction
In this report I will load stock tickers from an excel file in order to use the tickers when downloading historical price data for each stock. So firstly I will use the xlrd-library in order to open and retrieve excel-data. Secondly I will use Maik Rosenheinrich beautiful functions that enables talking to Yahoo-finance in order to retrieve price-data *(see his blogpost at [blogpost](https://maikros.github.io/yahoo-finance-python/))*. Lastly I will manipulate the data in order to only "store" close prices together with daily returns.


# Method
## Importing tickers from excel-file
The procedure to fetch data from an excel file is of course identical with the one presented in the earlier post, i.e.
```{python, python.reticulate = TRUE}
import xlrd
import pandas as pd

excel_dir = "../../static/excelfiles/tickers.xlsx"
wb = xlrd.open_workbook(excel_dir)
sh = wb.sheet_by_name('Data')

Tickers = []
for i in range(1, sh.nrows):
  Tickers.append(sh.cell_value(i,0))
```

and the result, as before, looks like this

```{r, echo = FALSE, results = "show"}
py$Tickers %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Scraping functions
Now lets define a function that fetch stock prices using Yahoo-finance API.
The function follows, together with a function that transforms the list of data into a pandas dataframe.
```{python, python.reticulate = TRUE}
from bs4 import BeautifulSoup
import re

def _get_crumbs_and_cookies(stock):
    
    url = 'https://finance.yahoo.com/quote/{}/history'.format(stock)
    with requests.session():
        header = {'Connection': 'keep-alive',
                   'Expires': '-1',
                   'Upgrade-Insecure-Requests': '1',
                   'User-Agent': 'Mozilla/5.0 (Windows NT 10.0; WOW64) \
                   AppleWebKit/537.36 (KHTML, like Gecko) Chrome/54.0.2840.99 Safari/537.36'
                   }
        
        website = requests.get(url, headers=header)
        soup = BeautifulSoup(website.text, 'lxml')
        crumb = re.findall('"CrumbStore":{"crumb":"(.+?)"}', str(soup))

        return (header, crumb[0], website.cookies)
```

Now we write a function to transform the dates into unix timestamps since Yahoo-Finance demands this format in the URL-request

```{python, python.reticulate = TRUE}
from datetime import datetime
from time import mktime

def convert_to_unix(date):
    datum = datetime.strptime(date, '%d-%m-%Y')
    
    return int(mktime(datum.timetuple()))
```

Since the data will be expressed in the comma separated list we write a function that interpreters the list and transform it into a pandas dataframe, the function follows:

```{python, python.reticulate = TRUE}
def list_to_dataframe(data, stock):
    headers = data[0].split(',')
    list = []
    for i in range(1, len(data)):
        list.append(data[i].split(','))
    try:
        df = pd.DataFrame(list, columns = headers)
        df['Ticker'] = stock
    except:
        df = pd.DataFrame(columns = headers)
        df['Ticker'] = stock
    return df
```

Now we can put these three functions into work together with a url request function in order to obtain the price data for each stock, the function follows:

```{python, python.reticulate = TRUE}
import requests

def load_stock_prices(stock, day_begin, day_end, interval='1d'):
    day_begin_unix = convert_to_unix(day_begin)
    day_end_unix = convert_to_unix(day_end)

    header, crumb, cookies = _get_crumbs_and_cookies(stock)
    
    with requests.session():
        url = 'https://query1.finance.yahoo.com/v7/finance/download/' \
              '{stock}?period1={day_begin}&period2={day_end}&interval={interval}&events=history&crumb={crumb}' \
              .format(stock=stock, day_begin=day_begin_unix, day_end=day_end_unix, interval=interval, crumb=crumb)
                
        website = requests.get(url, headers=header, cookies=cookies)
        data = website.text.split('\n')[:-1]
        dataframe = list_to_dataframe(data, stock)

        return dataframe
```


Now finally lets utilize our functions and scrape Yahoo-Finance for the data that we are after for each symbol/ticker

```{python, include = FALSE}
import pandas as pd
df_master = []
day_begin = "20-07-2018"
day_end = "31-07-2018"
for i in range(0, len(Tickers)):
  data = load_stock_prices(Tickers[i], day_begin, day_end)
  df_master.append(data)
  
prices = pd.concat(df_master, ignore_index = True)
```

```{r, echo = FALSE, results = "show"}
py$prices %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Result
Now we fill the null's with zeros and subsetting the dataframe into (**date, ticker, closeprice**)

```{python}
ClosePrices = prices[['Date', 'Ticker', 'Close']]
ClosePrices = pd.DataFrame(ClosePrices)
ClosePrices[ClosePrices['Close'] == 'null'] = 0.0
ClosePrices[ClosePrices['Close'] == 'null']
#ClosePrices['Date'] = pd.to_datetime(ClosePrices['Date'], errors='coerce')
ClosePrices = ClosePrices.dropna(subset=['Date'])
ClosePrices = ClosePrices.fillna(0.0)
```

```{python, include = FALSE}
ClosePrices['Date'] = pd.to_datetime(ClosePrices['Date']).dt.date
ClosePrices['Ticker'] = ClosePrices.Ticker.astype(str)
ClosePrices['Close'] = ClosePrices.Close.astype(float)
ClosePrices.dtypes
```


```{r, echo = FALSE, results = "show"}
py$ClosePrices %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Finally we calculate the daily returns, based on the daily close-price

```{python}
#ClosePrices = ClosePrices.sort_values(['Ticker','Date']).reset_index(drop = True)
ClosePrices['Return'] = ClosePrices.groupby('Ticker')['Close'].pct_change()
ClosePrices = ClosePrices.dropna()
```

```{r, echo = FALSE, results = "show"}
py$ClosePrices %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```
  kable_styling(bootstrap_options = c("striped", "hover"))
